An IFS study of Low-powered Radio Galaxies

### 2018-01-26 paper.tex
EoDC: Draft 0.9.1
Have done a read through and correction. Still waiting for uni comp to
run MUSE plots.

Corrected emission line maps

 On branch master
 Changes to be committed:
	modified:   paper.tex
	modified:   produce_maps.py

% Abstract of the paper
\begin{abstract}
This is a simple template for authors to write new MNRAS papers.
The abstract should briefly describe the aims, methods, and main results of the paper.
It should be a single paragraph not more than 250 words (200 words for Letters).
No references should appear in the abstract.
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
% keyword1 -- keyword2 -- keyword3
\end{keywords}

@@

\section{Introduction}
	\label{sec:intro}
	% There are known to be strong scaling relations between the mass of the central supermassive black-hole (SMBH) and the global properties in a given galaxy, such as velocity dispersion, the $M-\sigma$ relation \citep{Ferrarese2000, Gebhardt2000, Graham2011}; Sersic index \citep{Graham2007, Savorgnan2013}; luminosity \citep{Laor2001, McLure2001, Lauer2007, Graham2012}; etc. AGN feedback is understood to be the mechanism by which the SMBH can expand its sphere of influence to galactic scales to affect these relationship.

	% This is generally understood to be a feedback process, where large amounts of gas within the galaxy cools, falls on the SMBH. Here the black-hole imparts energy to the gas, causing outflows (or jets) and/or thermal emission. We observe this as an Active Galactic Nuclei (AGN) which can have distinctive emission across the electromagnetic spectrum. The exact mechanisms of imparting energy still remains an open question, with much theoretical and observational work ongoing. The outflows can then effect the outer parts of the galaxy, by methods such as fountain effects \citep{}, thermal heating \citep{DeYoung2010} and shocks created by the outflows \citep{}.

	% One identifier of AGNs is a radio signature consistent with Synchrotron emission from the outflow i.e a radio galaxy (RG). These are typically categorized into one of two classes: Fanaroff-Riley (FR) I or FR II \citep{Fanaroff1974}. Of these we focus on the former since these are by far the most common mode in the local universe (possibly as far as $z \sim 1$ \citep{Rigby2008}), and so to discuss radio AGN feedback is to consider feedback from FR I sources \citep{DeYoung2010}. Indeed, while there is broad consensus \citep{Heckman1986, Baum1992} that the brightest RGs (mostly FR IIs) are caused when a massive galaxy merges with a gas rich galaxy (a wet merger) giving a plentiful fuel reservoir to the AGN \citep{Baum1992}, there is much more debate when it comes to low-powered ($P_\text{1.4 GHz} \lesssim 10^{24.5} \, \mathrm{W Hz^{-1}}$) RGs (mostly FR I). Suggestions fall into two categories: an extrapolation of radio-loud galaxies (i.e. a merger with either small gas reservoirs or low efficiency accretion onto the SMBH) or a highly efficient accretion of gas from secular origins (such as Bondi accretion of the hot X-ray component of the Inter-Stellar Medium (ISM) \citep{Allen2006} or from existing cold gas reservoirs \citep{Prandoni2010}). This project aims to add to this discussion using Integral Field Unit (IFU) observations in the visible band of nearby radio galaxies and comparing this with Atlas-3D sample \citep{Cappellari2011} as a control sample.

% More to add to intro - e.g. summery of paper

	We refer to the combined Atlas$^\text{3D}$ and MASSIVE sample as the A+M sample.

@@

	\begin{table*}
		\centering
	% \begin{threeparttable}
		\caption{Key sample characteristics of the Southern Sample galaxies. Col.\,1: host galaxy name. Col.\,2: radio source name from Parkes Southern Radio Source Catalogue. We hereafter refer to the last galaxy by its PKS name only. Col.\,3: redshift. Col.\,4: National Radio Astronomy Observatory (NRAO) Very Large Array (VLA) Sky Survey (NVSS) 1.4 GHz flux density \citep{Condon1998}. Col.\,5: Two Micron All Sky Survey (2MASS) $K$-band apparent magnitude (with errors of $\pm 0.025$ mag; \citealt{Skrutskie2006}). Col.\,6: dust morphologies from (a) \citet{Govoni2000}, (b) \citet{Lauer2005}, (c) \citet{Bettoni2001}, (d) \citet{Sandage1979}, (e) \citet{Colbert2001}.}
		\label{tab:sample}
		\begin{tabular}{l c c c c l}
			\hline
			\hline
			Host galaxy	& Radio source 	& Redshift	& $S_\text{1.4\,GHz}$	& $m_K$ & Dust morphology\\
						& (PKS) 		& 			& (mJy) 			& (mag)	&\\
			\hline 
			ESO 443-G024 & 1258-321 	& 0.01703	& $1387 \pm 45$		& 8.51 & no dust\tnote{a}	\\ 
			IC 1459 	& 2254-367 		& 0.00565 	& $1280 \pm 45$		& 6.81 & dust lane\tnote{b}	\\
			IC 1531 	& 0007-325 		& 0.02553 	& \leavevmode\phantom{0}$388 \pm 12$		& 9.55 & --					\\
			IC 4296		& 1333-\leavevmode\phantom{0}33 		& 0.01248 	& $1342 \pm 41$		& 7.50 & edge-on disc\tnote{b} \\
			NGC 612 	& 0131-\leavevmode\phantom{0}36 		& 0.02954 	& \leavevmode\phantom{0}$585 \pm 18$		& 9.58 & dust lane\tnote{c}	\\
			NGC 1316 	& 0320-\leavevmode\phantom{0}37 & 0.00591 	& \leavevmode\phantom{0}$255 \pm 10$		& 5.59 & dust patches\tnote{b} \\
			NGC 1399 	& 0336-\leavevmode\phantom{0}35 & 0.00472 	& \leavevmode\phantom{0}$209 \pm \leavevmode\phantom{0}7$	& 6.31 & no dust\tnote{b}	\\
			NGC 3100 	& 0958-314 		& 0.00879 	& \leavevmode\phantom{0}$530 \pm 16$		& 8.08 & dust lane\tnote{d}	\\
			NGC 3557 	& 1107-372 		& 0.01016 	& \leavevmode\phantom{0}$484 \pm 16$		& 7.20 & face-on disc\tnote{b}\\
			NGC 7075 	& 2128-388 		& 0.01819 	& \leavevmode\phantom{0}$837 \pm 28$		& 9.56 & --					\\
			--			& 0718-\leavevmode\phantom{0}34 		& 0.02897 	& $1119 \pm 41$		& 9.97 & dust patches\tnote{e} \\
			\hline
			\hline
		\end{tabular}
	% 	\begin{tablenotes}
	% 	\footnotesize
	% 	\note Col.\,1: host galaxy name. Col.\,2: radio source name from Parkes Southern Radio Source Catalogue. Col.\,3: redshift. Col.\,4: National Radio Astronomy Observatory (NRAO) Very Large Array (VLA) Sky Survey (NVSS) 1.4 GHz flux density \citep{Condon1998}. Col.\,5: Two Micron All Sky Survey (2MASS) $K$-band apparent magnitude (with errors of $\pm 0.025$ mag; \citealt{Skrutskie2006}). Col.\,6: dust morphologies from (a) \citet{Govoni2000}, (b) \citet{Lauer2005}, (c) \citet{Bettoni2001}, (d) \citet{Sandage1979}, (e) \citet{Colbert2001}. 
	% 	\item We hereafter refer to the last galaxy by its PKS name only.
	% 	\end{tablenotes}
	% \end{threeparttable}
	\end{table*}

	These criteria lead to a sample of 11 galaxies hereafter referred to as the Southern Sample. The key observed characteristics are summarised in Table \ref{tab:sample}.
	%, while the derived characteristics are listed in Table \ref{tab:sampleDerived}. 
	All galaxies have a FR I radio morphology according to the \citet{Fanaroff1974} scheme; the bulk of the radio emission is centrally-concentrated, as opposed to the FR II morphology where the brightest points are at the ends of the radio lobes.

@@

\section{Observing strategy and Data Reduction}
	\label{sec:obs}
	The sample was observed with the Visible Multi-Object Spectrograph (VIMOS), mounted on UT3 on the VLT in Paranal \citep{LeFevre2003}. All observations were taken with a spatial sampling of $0\farcs67$, using the high-resolution blue grism yielding a wavelength range of 3700-5520\,\AA\ with a spectral resolution of 1440 and sampling of 0.71\,\AA\,$\mathrm{pix^{-1}}$. Each object was observed with a total integration time of $\approx 100$\,min on-source, equally spread over three observing blocks (OBs). Each OB also contained all the necessary observation for standard IFS data reduction.

	VIMOS has several well-known though poorly-understood technical issues. These include several low transmission (bad) fibres, strong flexure, contamination from adjacent spectra on the CCD (cross-talk) and large differences in sensitivity across its 4 quadrants. To address these issues, we adopted a data-reduction pipeline produced using \textsc{Py3D}, a suite of programs based on the \textsc{python} versions of those developed for the Calar Alto Legacy Integral Field spectroscopy Area survey \citep[CALIFA;][]{Sanchez2012, Husemann2013} but later updated for VIMOS by \citet{Husemann2014}. \textsc{Py3D} applies all standard IFS data-reductions steps: bias subtraction, spectrum identification, flatfielding and wavelength calibration. In addition, the data was flux calibrated using publicly available observations of the spectro-photometric standard star Feige 110 provided by ESO. All steps include methods to account for the bad fibres, flexure and cross-talk within VIMOS.

	Following this, we noted that the cubes where still not properly calibrated. Three main issues remain: the quadrants have different intensities, clearly showing uncorrected throughput differences; diagonal intensity stripes are present in the reconstructed images at all wavelengths; and spectral features are observed \citep{Jullo2008} that are visually similar to fringe patterns caused by interference within the CCD between incident light and light reflected from the interfaces between layers of the CCD materials. \citet{Lagerholm2012} present ad-hoc methods to correct for these issues, which we here adopt. These additional steps mean that the datacubes are not perfectly flux-calibrated, but all the corrections are multiplicative and thus will not effect equivalent width or line ratio measurements. From comparisons to the MUSE data (see Section \ref{subsec:MUSE}), we then estimate the flux calibration of the resulting datacubes.

	These method are not completely effective and some artefacts are still present in the data, however in most cases the data is of sufficient quality for our purposes. For the worst effected datacubes, we have archival observations (see Section \ref{subsec:MUSE}).

@@

	\subsection{MUSE Archival Data}
		\label{subsec:MUSE}
		Four of the sample galaxies are in the Multi-unit Spectroscopic Explorer (MUSE) archive: IC 1459, IC 4296, NGC 1316 and NGC 1399. We include these in our analysis as they have better (spatial and spectral) resolution and sampling, a larger field-of-view and larger wavelength range than the VIMOS data.

		We used the pre-reduced (Phase 3) datacubes from ESO. These were generally of sufficient quality for our purpose, except in both IC 1459 and IC 4296 the sky appears to have been over-subtracted. To remove this over-subtraction, we developed our own pseudo-sky subtraction routine. A median spectrum was taken from four $20 \times 20$\,spaxel regions, one in from each spatial corner of the ESO reduced cube. After checking that no stellar continuum could be fit to the medium sky spectrum (i.e.\ that very little light from the galaxy is contaminating the pseudo-sky regions), this median sky spectrum was subtracted from each spaxel in the cube.

@@

\section{Data Analysis}
	\label{sec:analysis}
	From this point on, the VIMOS and MUSE datasets are treated almost identically, the only difference (other than the different spectral ranges and resolutions) being that the MUSE datacubes are spatially binned to a higher signal-to-noise ratio (S/N) using Voronoi binning\footnote{http://www-astro.physics.ox.ac.uk/~mxc/software/} \citep{Cappellari2003}. For our purposes, we define the `signal' and `noise' of each spaxel as the median value of its spectrum and noise spectrum, respectively. We require a S/N of 30 for all VIMOS datacubes and 50 for the IC 1459 and IC 4296 MUSE datacubes. The NGC 1316 and NGC 1399 MUSE datacubes were binned to a S/N of 50 for the analysis of the stellar kinematics and 100 for the analysis of the emission line kinematics and stellar populations.

	Next we implement a routine to find optimal initial guesses of the redshift and velocity dispersion for each galaxy, to be used when fitting individual bins, by means of iterative fits to the spatially collapsed (i.e. summed across both spatial dimensions of the datacube) spectrum. We use the penalized-fitting (\textsc{pPXF}) routine\footnote{http://www-astro.physics.ox.ac.uk/~mxc/software/} of \citet{Cappellari2004} and \citet{Cappellari2016a} with the Medium-resolution Issac Newton Telescope (INT) Library of Empirical Spectra (MILES) library \citep{Sanchez-Blazquez2006, Falcon-Barroso2011a} to find the best-fitting line-of-sight velocity distribution (LOSVD; as parametrised by the Gaussian parameters $v$, the mean velocity and $\sigma$, the velocity dispersion). The final mean velocity of a given galaxy, is used as its precise spectroscopic redshift and is given in Table \ref{tab:sample}. Beyond this point, each bin is analysed independently.

	\subsection{Stellar Kinematics}
		\label{subsec:starKin}
		Each bin is fit independently again using \textsc{pPXF} with the MILES library. For the fit, regions around potential emission lines (list below) are masked, and a fourth order polynomial additive continuum correction is used. A Monte--Carlo (MC) estimate of the uncertainties is used.

	\subsection{Ionized Gas Distribution and Kinematics}
		\label{subsec:EmissionLines}
		We fit the ionized gas fluxes and kinematics for the emission lines [\ion{O}{ii}], H$\delta$, H$\gamma$, H$\beta$, [\ion{O}{iii}], [\ion{N}{I}], [\ion{O}{i}], [\ion{N}{ii}], H$\alpha$ and [\ion{S}{ii}] using Gaussian templates. This independently fits emission lines from the interstellar medium (ISM), with a single LOSVDs (again parametrised by the Gaussian parameters $v$, the mean velocity and $\sigma$, the velocity dispersion), independently of the stellar kinematics. In the cases of the [\ion{O}{iii}], [\ion{O}{i}] and [\ion{N}{ii}] doublets, the two components of the doublets are fit with a fixed flux ratio of 1:0.34. The [\ion{N}{i}] doublet has a fixed ratio of 1:0.65 \citep{Safier1992}. The two components of the [\ion{O}{ii}] and [\ion{S}{ii}] doublets are fit independently. To minimize template mismatch, whereby emission lines are erroneously fitted to the edges of badly modeled and thus subtracted absorption features, we follow the method set out in \citet{Sarzi2005}, whereby the stellar component is first fitted as above with masked potential emission line regions, followed by the unmasking and fitting of the [\ion{O}{iii}] doublet which sets the kinematics for all the emission lines and finally the amplitude of the remaining emission lines. %Some of the forbidden emission lines have the ratio of their amplitudes fixed (see Table \ref{tab:EmissionLine}, Col.\,4).

@@

	\subsection{Absorption Line Strengths}
		\label{subsec:absorption}
		Due to the lack of calibration observations of Lick/Cassegrain Image Dissector Scanner spectrograph system (hereafter Lick/IDS system; \citealt{Faber1985, Worthey1994}) we use the line index system (LIS) of \citet{Vazdekis2010} instead. This relies on flux calibrations instead of correcting to the continuum shape and wavelength dependent resolution of the Lick/IDS system. We use the index definitions of \citet{Trager1998}, measuring the following indices: G4300, Fe4383, Ca4455, Fe4531, H\,$\beta$, Fe5015, Mg\,b, Fe5270, Fe5335, Fe5406, Fe5709, Fe5782, NaD, TiO1 and TiO2. TiO1 and TiO2 are considered molecular absorption lines and are measured in magnitude units, while all others are atomic and measured in angstroms.

		Quoted line strengths are corrected for both emission line and the effect of the velocity dispersion of the stars. These corrections are detailed below.

@@

		\subsubsection{Correcting for Stellar Velocity Dispersion}
			\label{subsubsec:EmissionFit}
			We correct for the effect of the different velocity dispersions of the stars which varyingly spread absorption features such that differing fractions of the absorption is outside of the central bandpasses. To do this, we create a best-fitting spectrum (as in the previous step) which is \textit{not} convolved with the best-fitting LOSVD. A given index, $I$, is then measured for both this `unconvolved' spectrum ($I^\text{unc}$) and the convolved best-fitting spectrum ($I^\text{conv}$), and the ratio of these two indices is used as a multiplicative correction factor for the index measured ($I^\text{obs}$), such that the corrected index ($I^\text{corr}$) is given by
			\begin{equation}
				I^\text{corr} \equiv \frac{I^\text{unc}}{I^\text{conv}} I^\text{obs} \, .
			\end{equation}
			These corrected indices are those reported and discussed in the sections below.

@@

	\subsection{Regular/Non-regular Rotators}
		We find 4/11, or $(36\pm15)$\%, of our sample galaxies are regular rotators. This compares to 82\% of the Atlas$^\text{3D}$ sample being classified as regular rotators \citep{Krajnovic2011}. However the likely-hood of a given galaxy being a regular rotator is highly mass dependent with the likely-hood decreasing with increasing mass. Thus since our Southern sample are all extremely massive galaxies, we expect to find a higher fraction of non-regular rotators than the Atlas$^\text{3D}$ survey.

@@

The Acknowledgements section is not numbered. Here you can thank helpful
colleagues, acknowledge funding agencies, telescopes and facilities used etc.
Try to keep it short.

>>>>

% Abstract of the paper
\begin{abstract}
The most powerful radio galaxies are well studied with a strong consensus in the literature regarding their formations processes. However they are intrinsically rare objects and not representative of the general population of radio galaxies. Low-powered radio galaxies are comparatively poorly studied with many conflicting viewpoints regarding their origin and the extent of the effect of feedback from them.

In this paper, we present a complete sample of 11 nearby low-powered radio galaxies, observed with a suite of instruments. This paper focuses on the spatially-resolved stellar kinematics, stellar populations, and ionized gas distribution, kinematics and ionization derived from optical IFS observations, while other observation such as \ce{^{12}CO(2-1)} from Atacama Large Millimeter/sub-millimeter Array (ALMA) and radio continuum from the Very Large Array (VLA) will be presented in future papers, but are overlaid on our maps (cyan and red contours respectively, in Figs \ref{fig:eso443}-\ref{fig:pks718}). We compare the characteristics and properties of our sample to those of ordinary (i.e.\ optically-selected) ETGs using the Atlas$^\text{3D}$ and MASSIVE IFS surveys. These include the fast/slow rotator classification fraction, kinematic substructures, absorption line strength radial gradients, general stellar population properties, ionized gas distribution and kinematics and the dominant source of ionizing photons.

We tentatively find that our radio-selected ETGs contain a higher mass in of ionized gas than expected, but after accounting for the differences in the mass distribution, we find no further differences between the two samples in the characteristics that can be studied with optical IFU data. We suggest that this is consistent with the notion that low-powered radio galaxies are ordinary ETGs experiencing a brief active phase which maintains their low star-formation rates (also known as maintenance or jet-mode AGN). 
\end{abstract}

\begin{keywords}
galaxies: kinematics and dynamics -- galaxies: abundances -- galaxies: active -- galaxies: jets -- galaxies: structure
\end{keywords}

@@

\section{Introduction}
	\label{sec:intro}
	It is becoming increasingly clear that two different types of active galactic nuclei (AGN) exist, radiative and jet mode AGN \citep[e.g.][]{Antonucci2012, Heckman2014}, raising speculation about differing mechanisms and possibly fuel sources for each. The former is thought to be the powerful engine that initially and rapidly shuts off star formation in massive early-type galaxies (ETGs; e.g. \citealt{Thomas2005, Thomas2010}), either by removing the cold gas from the galaxy entirely, heating it such that it joins the hot X-ray gas often present in massive galaxies \citep[e.g.][]{OSullivan2001}, or rendering it unusable for star formation (such as by stabilising it against collapse; e.g.\ \citealt{Martig2009}). After a single radiative-mode episode, the AGN is thought to subside to become jet-dominated, repeatedly reheating the surrounding interstellar medium (ISM) to counter any cooling that might allow the cold gas reservoir to replenish (and subsequently form stars).

	There is a strong consensus within the scientific literature that the most powerful radio galaxies are the result of gas-rich, major mergers causing large amounts of material to fall on to the black hole at the centre of the resulting galaxy, thus producing an immensely powerful AGN which includes a powerful radio jet \citep[e.g.][]{Malin1983, Quillen1992, Lim2000}. However, such galaxies are by construction extremely rare and are not representative of the general radio galaxy population. Most radio galaxies are low-powered, and their basic properties and origins are poorly constrained. One of the most popular suggestions is that they are bona-fide detections of jet-mode AGN.%, a class of AGN thought to maintain the dearth of star formation in early-type galaxies (ETGs), after most of the fuel for star formation has been removed by an earlier event. 
	These radio galaxies are known to be dusty with dust lanes having a tendency to be perpendicular to the jets \citep[e.g.][]{DeRuiter2002, VerdoesKleijn2005}. They have little ionized gas in the ISM \citep[e.g.][]{}, but often have significant quantities of hot X-ray gas (e.g. \citealt{}; the cold phase of the ISM of radio galaxies will be examined in Ruffa et.al.\ in prep.). If the low star-formation rates typically seen in massive ETGs are preserved by jet-mode AGN, then all such ETGs must regularly go through similar active phases, and therefore low-powered radio galaxies should be much the same as their radio-quiet (quiescent phase) ETG counterparts.

	To test this hypothesis, a complete sample of 11 nearby low-powered radio galaxies was constructed \citep{} and observed with a suite of instruments. Here, we present the spatially-resolved stellar kinematics, stellar populations, and ionized gas distribution, kinematics and ionization derived from integral-field spectroscopic (IFS) observations with the Visible Multi-object Spectrograph (VIMOS) and archival data from the Multi-unit Spectroscopic Explorer (MUSE), both on the Very Large Telescope (VLT). We compare the characteristics and properties (accessible with $V$-band IFS data) of our sample of low-power radio galaxies to those of ordinary (i.e.\ optically-selected) ETGs from the Atlas$^\text{3D}$ and MASSIVE IFS surveys. We hereafter refer to the combined Atlas$^\text{3D}$ and MASSIVE sample as the A+M sample.

	In Section \ref{sec:samp} we, set out the compete sample with our observations and data-reduction methods detailed in Section \ref{sec:obs}. Our data-analysis methods and routines are detailed in Section \ref{sec:analysis} (the maps of our sample produced with these methods are shown in Appendix \ref{sec:maps}). We present our findings regarding the stellar kinematics, absorption line strengths, stellar populations, ionized gas (distribution, kinematics and ionization) in Sections \ref{sec:StarKine}-\ref{sec:gas}, respectively. Finally, we discuss our results and conclude in Section \ref{sec:discuss}.

@@

	\begin{table*}
		\centering
	% \begin{threeparttable}
		\caption{Key characteristics of the Southern Sample galaxies. Col.\,1: host galaxy name. Col.\,2: radio source name from Parkes Southern Radio Source Catalogue. We hereafter refer to the last galaxy by its PKS name only. Col.\,3: redshift. Col.\,4: National Radio Astronomy Observatory (NRAO) VLA Sky Survey (NVSS) 1.4 GHz flux density \citep{Condon1998}. Col.\,5: Two Micron All Sky Survey (2MASS) $K$-band apparent magnitude (with errors of $\pm 0.025$ mag; \citealt{Skrutskie2006}). Col.\,6: dust morphologies from (a) \citet{Govoni2000}, (b) \citet{Lauer2005}, (c) \citet{Bettoni2001}, (d) \citet{Sandage1979}, (e) \citet{Colbert2001}.}
		\label{tab:sample}
		\begin{tabular}{l c c c c l}
			\hline
			\hline
			Host galaxy	& Radio source 	& Redshift	& $S_\text{1.4\,GHz}$	& $m_K$ & Dust morphology\\
						& (PKS) 		& 			& (mJy) 			& (mag)	&\\
			\hline 
			ESO 443-G024 & 1258-321 	& 0.01703	& $1387 \pm 45$		& 8.51 & no dust\tnote{a}	\\ 
			IC 1459 	& 2254-367 		& 0.00565 	& $1280 \pm 45$		& 6.81 & dust lane\tnote{b}	\\
			IC 1531 	& 0007-325 		& 0.02553 	& \leavevmode\phantom{0}$388 \pm 12$		& 9.55 & --					\\
			IC 4296		& 1333-\leavevmode\phantom{0}33 		& 0.01248 	& $1342 \pm 41$		& 7.50 & edge-on disc\tnote{b} \\
			NGC 612 	& 0131-\leavevmode\phantom{0}36 		& 0.02954 	& \leavevmode\phantom{0}$585 \pm 18$		& 9.58 & dust lane\tnote{c}	\\
			NGC 1316 	& 0320-\leavevmode\phantom{0}37 & 0.00591 	& \leavevmode\phantom{0}$255 \pm 10$		& 5.59 & dust patches\tnote{b} \\
			NGC 1399 	& 0336-\leavevmode\phantom{0}35 & 0.00472 	& \leavevmode\phantom{0}$209 \pm \leavevmode\phantom{0}7$	& 6.31 & no dust\tnote{b}	\\
			NGC 3100 	& 0958-314 		& 0.00879 	& \leavevmode\phantom{0}$530 \pm 16$		& 8.08 & dust lane\tnote{d}	\\
			NGC 3557 	& 1107-372 		& 0.01016 	& \leavevmode\phantom{0}$484 \pm 16$		& 7.20 & face-on disc\tnote{b}\\
			NGC 7075 	& 2128-388 		& 0.01819 	& \leavevmode\phantom{0}$837 \pm 28$		& 9.56 & --					\\
			--			& 0718-\leavevmode\phantom{0}34 		& 0.02897 	& $1119 \pm 41$		& 9.97 & dust patches\tnote{e} \\
			\hline
			\hline
		\end{tabular}
	% 	\begin{tablenotes}
	% 	\footnotesize
	% 	\note Col.\,1: host galaxy name. Col.\,2: radio source name from Parkes Southern Radio Source Catalogue. Col.\,3: redshift. Col.\,4: National Radio Astronomy Observatory (NRAO) Very Large Array (VLA) Sky Survey (NVSS) 1.4 GHz flux density \citep{Condon1998}. Col.\,5: Two Micron All Sky Survey (2MASS) $K$-band apparent magnitude (with errors of $\pm 0.025$ mag; \citealt{Skrutskie2006}). Col.\,6: dust morphologies from (a) \citet{Govoni2000}, (b) \citet{Lauer2005}, (c) \citet{Bettoni2001}, (d) \citet{Sandage1979}, (e) \citet{Colbert2001}. 
	% 	\item We hereafter refer to the last galaxy by its PKS name only.
	% 	\end{tablenotes}
	% \end{threeparttable}
	\end{table*}

	These criteria lead to a sample of 11 galaxies hereafter referred to as the Southern Sample. The key observed characteristics are summarised in Table \ref{tab:sample}. All galaxies have a FR I radio morphology according to the \citet{Fanaroff1974} scheme.

@@

\section{Observing strategy and Data Reduction}
	\label{sec:obs}
	The sample was observed with VIMOS, mounted on the VLT in Paranal \citep{LeFevre2003}. All observations were taken with a spatial sampling of $0\farcs67$, using the high-resolution blue grism yielding a wavelength range of 3700-5520\,\AA\ with a spectral resolution of 1440 and sampling of 0.71\,\AA\,$\mathrm{pix^{-1}}$. Each object was observed with a total integration time of $\approx 100$\,min on-source, equally spread over three observing blocks (OBs). Each OB also contained all the necessary observation for standard IFS data reduction.

	VIMOS has several well-known though poorly-understood technical issues. These include several low transmission (bad) fibres, strong flexure, contamination from adjacent spectra on the CCD (cross-talk) and large differences in sensitivity across its 4 quadrants. To address these issues, we adopted a data-reduction pipeline produced using \textsc{Py3D}, a suite of programs based on the \textsc{python} versions of those developed for the Calar Alto Legacy Integral Field spectroscopy Area survey \citep[CALIFA;][]{Sanchez2012, Husemann2013} but later updated for VIMOS by \citet{Husemann2014}. \textsc{Py3D} applies all standard IFS data-reductions steps: bias subtraction, spectrum identification, flatfielding and wavelength calibration. In addition, the data was flux calibrated using publicly available observations of the spectro-photometric standard star Feige 110 provided by the European Southern Observatory (ESO). All steps include methods designed to account for the bad fibres, flexure and cross-talk within VIMOS.

	Following this, we noted that the cubes were still not properly calibrated. Three main issues remain: the quadrants have different intensities, clearly showing uncorrected throughput differences; diagonal intensity stripes are present in the reconstructed images at all wavelengths; and spectral features are observed \citep{Jullo2008} that are visually similar to fringe patterns caused by interference within the CCD between incident light and light reflected from the interfaces between layers of the CCD materials. \citet{Lagerholm2012} present ad-hoc methods to correct for these issues, which we here adopt. These additional steps mean that the datacubes are not perfectly flux-calibrated, but all the corrections are multiplicative and thus will not effect equivalent width or line ratio measurements. From comparisons to the MUSE data (see Section \ref{subsec:MUSE}), we then estimate the flux calibration of the resulting datacubes.

	These method are not completely effective and some artefacts are still present in the data, however in most cases the data is of sufficient quality for our purposes. For the worst effected datacubes, we have archival MUSE observations (see Section \ref{subsec:MUSE}).

@@

	\subsection{MUSE Archival Data}
		\label{subsec:MUSE}
		Four of the sample galaxies are in the MUSE archive: IC 1459, IC 4296, NGC 1316 and NGC 1399. We include these in our analysis as they have better (spatial and spectral) resolution and sampling, a larger field-of-view and larger wavelength range than the VIMOS data.

		We used the pre-reduced (Phase 3) datacubes from ESO. These were generally of sufficient quality for our purpose, except in both IC 1459 and IC 4296 the sky appears to have been over-subtracted. To remove this over-subtraction, we developed our own pseudo-sky subtraction routine. A median spectrum was taken from four $20 \times 20$\,spaxel regions, one in each spatial corner of the ESO reduced cube. After checking that no stellar continuum could be fit to the medium sky spectrum (i.e.\ that very little light from the galaxy is contaminating the pseudo-sky regions), this median sky spectrum was subtracted from each spaxel in the cube.

@@

\section{Data Analysis}
	\label{sec:analysis}
	Both VIMOS and MUSE datasets are spatially binned using Voronoi binning\footnote{\label{fn:Cappellari}http://www-astro.physics.ox.ac.uk/\~mxc/software/} \citep{Cappellari2003} and from this point on are treated almost identically, the only difference (other than the different spectral ranges and resolutions) being that the MUSE datacubes are spatially binned to a higher signal-to-noise ratio (S/N). For our purposes, we define the `signal' and `noise' of each spaxel as the median value of its spectrum and noise spectrum, respectively. We require a S/N of 30 for all VIMOS datacubes and 50 for the IC 1459 and IC 4296 MUSE datacubes. The NGC 1316 and NGC 1399 MUSE datacubes were binned to a S/N of 50 for the analysis of the stellar kinematics and 100 for the analysis of the emission line kinematics and stellar populations.

	Next we implement a routine to find optimal initial values of the redshift and velocity dispersion for each galaxy, to be used when fitting individual bins, by means of iterative fits to the spatially collapsed (i.e. summed across both spatial dimensions of the datacube) spectrum. We use the penalized-fitting (\textsc{pPXF}) routine\footnotemark[\ref{fn:Cappellari}] of \citet{Cappellari2004} and \citet{Cappellari2016a} with the Medium-resolution Issac Newton Telescope (INT) Library of Empirical Spectra (MILES) library \citep{Sanchez-Blazquez2006, Falcon-Barroso2011a} to find the best-fitting line-of-sight velocity distribution (LOSVD; as parametrised by the Gaussian parameters $v$, the mean velocity and $\sigma$, the velocity dispersion). The final mean velocity of a given galaxy, is used as its precise spectroscopic redshift and is given in Table \ref{tab:sample}. Beyond this point, each bin is analysed independently.

	\subsection{Stellar Kinematics}
		\label{subsec:starKin}
		Each bin is fit independently, again using \textsc{pPXF} with the MILES library. For the fit, regions around potential emission lines (listed in Section \ref{subsec:EmissionLines}) are masked, and a fourth order polynomial additive continuum correction is used. A Monte--Carlo (MC) estimate of the uncertainties is used.

	\subsection{Ionized Gas Distribution and Kinematics}
		\label{subsec:EmissionLines}
		In this analysis we consider the following emission lines and doublets: [\ion{O}{ii}]$\lambda\lambda$3726,3729, H$\delta$, H$\gamma$, H$\beta$, [\ion{O}{iii}]$\lambda\lambda$4969,5007, [\ion{N}{I}]$\lambda\lambda$5199,5202, [\ion{O}{i}]$\lambda\lambda$6300,6363, [\ion{N}{ii}]$\lambda\lambda$6548,6583, H$\alpha$ and [\ion{S}{ii}]$\lambda\lambda$6716,6731. We fit the fluxes and kinematics for the emission lines using Gaussian templates, independently fitting the emission lines of the ISM, with a single LOSVDs (again parametrised by the Gaussian parameters $v$, the mean velocity and $\sigma$, the velocity dispersion), from the stellar kinematics. In the cases of the [\ion{O}{iii}], [\ion{O}{i}] and [\ion{N}{ii}] doublets, the two components of the doublets are fit with a fixed flux ratio of 3:1. The [\ion{N}{i}] doublet has a fixed ratio of 3:2 \citep{Safier1992}. The two components of the [\ion{O}{ii}] and [\ion{S}{ii}] doublets are fit independently. To minimize template mismatch, whereby emission lines are erroneously fitted to the edges of badly modeled and thus subtracted absorption features, we follow the method set out in \citet{Sarzi2005}. In this method the stellar component is first fitted as above with masked potential emission line regions, followed by the unmasking and fitting of the [\ion{O}{iii}] doublet which sets the kinematics for all the emission lines and finally the amplitude of the remaining emission lines is fitted.

@@

	\subsection{Absorption Line Strengths}
		\label{subsec:absorption}
		Due to the lack of calibration observations of Lick/Cassegrain Image Dissector Scanner spectrograph system (hereafter Lick/IDS system; \citealt{Faber1985, Worthey1994}) standard galaxies, we use the line index system (LIS) of \citet{Vazdekis2010} instead. This relies on flux calibrations instead of correcting to the continuum shape and wavelength dependent resolution of the Lick/IDS system. We use the index definitions of \citet{Trager1998}, measuring the following indices: G4300, Fe4383, Ca4455, Fe4531, H\,$\beta$, Fe5015, Mg\,b, Fe5270, Fe5335, Fe5406, Fe5709, Fe5782, NaD, TiO1 and TiO2. %TiO1 and TiO2 are considered molecular absorption lines and are measured in magnitude units, while all others are atomic and measured in angstroms.

		Quoted line strengths are corrected for both emission line and the effect of the velocity dispersion of the stars as detailed below.

@@

		\subsubsection{Correcting for Stellar Velocity Dispersion}
			\label{subsubsec:EmissionFit}
			We correct for the effect of the different velocity dispersions of the stars which varyingly spread absorption features such that differing fractions of the absorption is outside of the central bandpasses. To do this, we create a stellar best-fitting spectrum which is \textit{not} convolved with the best-fitting LOSVD. A given index, $I$, is then measured for both this `unconvolved' spectrum ($I^\text{unc}$) and the convolved best-fitting spectrum ($I^\text{conv}$), and the ratio of these two indices is used as a multiplicative correction factor for the index measured ($I^\text{obs}$), such that the corrected index ($I^\text{corr}$) is given by
			\begin{equation}
				I^\text{corr} \equiv \frac{I^\text{unc}}{I^\text{conv}} I^\text{obs} \, .
			\end{equation}
			These corrected indices are those reported and discussed in the sections below.

@@

	\subsection{Regular/Non-regular Rotators}
		\label{subsec:RR}
		We find 4/11, or $(36\pm15)$\%, of our sample galaxies are regular rotators. This compares to 82\% of the Atlas$^\text{3D}$ sample being classified as regular rotators \citep{Krajnovic2011}. However the likely-hood of a given galaxy being a regular rotator is highly mass dependent with the likely-hood decreasing with increasing mass. Thus since our Southern sample are all extremely massive galaxies, we expect to find a higher fraction of non-regular rotators than the Atlas$^\text{3D}$ survey.

@@
